First, a huge thanks is in order for my advisor, David Hogg, for these years
of support, encouragement, and friendship.
I couldn't have imagined a better advisor for me and I'm looking forward to
many years of collaboration.
Hogg's enthusiasm is infectious and our lively discussions over lunch, coffee,
or beer have convinced me to attempt a career in academia and made me a better
scientist and person.

I would also like to thank my other dissertation readers, Jonathan Goodman and
Micheal Blanton, for taking the time to read my thesis and provide useful
suggestions and clarifications that improved the presentation of this work.

One of my favorite parts of studying astronomy is the community and the
opportunities to meet and get to know amazing people from around the world.
Over the course of my Ph.D.\ research, I have had the opportunity to
collaborate with more people than I can possibly list here.
I am especially grateful for the summers that I spent in Germany with Bernhard
Sch\"olkopf and Hans-Walter Rix; the garden chats in T\"ubingen and Heidelberg
were some of the highlights of my scientific career thus far.
I have also enjoyed and benefited from conversations and collaborations with
Brendon Brewer,
Tom Barclay,
Charlie Conroy,
Bekki Dawson,
Eric Ford,
Morgan Fouesneau,
Jonathan Goodman,
Dustin Lang,
Phil Marshall,
Ben Montet,
Tim Morton,
Mike O'Neil,
Adrian Price-Whelan,
Elisa Quintana,
Jonathan Sick,
Dan Weisz,
and many others.

My time spent living in NYC wouldn't have been the same without my eclectic
(and perfectly eccentric) group of housemates and friends.
In particular, I'd like to thank Mira, Stefan, Nate, Claire, Katherine, Jacob,
Silas, and Stumm for all the good times on Dean Street.
I would also like to thank Ruth for being there for me when I needed her and
sharing in life and in science, even from the opposite side of the ocean.

Finally, I would like to thank my family, Annie, Clarke, and Elaine for their
continued love, encouragement, and support every step of the way.
I would never have made it here without them!

\paragraph{Organizations}
The results in this dissertation are based, in large part, on observations
make by the \kepler\ Mission and subsequent \KT\ Mission with the same
instrument.
None of my work would have been possible without the tireless efforts of the
scientists and engineers on the \kepler\ team.
This work also relied heavily on the public data and literature resources
provided by the Mikulski Archive for Space Telescopes, the NASA Exoplanet
Archive, and the NASA Astrophysics Data System.

I would like to thank the organizers and attendees of the SAMSI workshop
``Modern Statistical and Computational Methods for Analysis of \kepler\
Data''.
This workshop introduced me to the \kepler\ data and drastically lowered the
barrier to entry into the field of exoplanets.
The connections made at this workshop have led to many important and
long-lasting friendships and collaborations.
